---
title: "MeToo_Final"
author: "Brier Gallihugh, B.S"
date: "1/7/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data input}
  library(car)
  library(pastecs)
  library(emmeans)
  library(psych)

MeTooData <- read.csv("Me Too Project_Cleaned_01_06.csv", header = TRUE)

RelevantData$CandidateIV <- MeTooData$Candidate_Condition
RelevantData$ParticipantIV <- MeTooData$Political.Leanings
RelevantData$SupportDV <- MeTooData$Your_Support_1
```

```{r assumptions}
#Normality Assumption for General Support
NormalityResiduals <- rstandard(aov(RelevantData$SupportDV ~ RelevantData$ParticipantIV * RelevantData$CandidateIV))
hist(AOVResid, col = 'lightgrey', 
     main="", xlab = "ANOVA Model Residuals",
     probability = TRUE)
curve(dnorm(x, mean = mean(AOVResid), 
            sd = sd(AOVResid)), 
            add = TRUE, lwd = 2, col = 'blue')
#Stat test for non-normal
describe(NormalityResiduals)

#Degree of Support
#Homogeneity of Variance for Degree Support (ParticipantAffiliation)
boxplot(RelevantData$SupportDV ~ RelevantData$ParticipantIV)
#Levene Test for Degree Support (ParticipantAffiliation)
leveneTest(y = RelevantData$SupportDV, group = RelevantData$ParticipantIV)
#Homogeneity of Variance for Degree Support (CandidateAffiliation)
boxplot(RelevantData$SupportDV ~ RelevantData$CandidateIV)
#Leven's Test for Degree of Support (CandidateAffiliation)
leveneTest(y = RelevantData$SupportDV, group = RelevantData$CandidateIV)
```


```{r analysis}
#Degree of Support (DV1)
SupportFit <- aov(RelevantData$SupportDV ~ RelevantData$ParticipantIV * RelevantData$CandidateIV)
summary(SupportFit)
#Effect Size
Anova(SupportFit, type = "III")
anova_stats(SupportFit)
#Post Hoc Interaction Effects
SupportPostHoc <- lsmeans(SupportFit,
                      pairwise ~ ParticipantIV:CandidateIV,
                      adjust="tukey")
summary(SupportPostHoc)
```

*Results*

Results indicated both a main effect of candidate affiliation on candidate support (*F* = 43.97, *p* < .001, $eta^2$ = .049) and a main effect of participant affiliation on candidate support (*F* = 9.98, *p* = .002, $eta^2$ = .121). Further, results also indicated an interaction effect of candidate and participant affiliation on candidate support (*F* = 30.19, *p* < .001, $eta^2$ = .077). A post hoc analysis using a Tukey adjustment indicated the following:

Main Effect (Candidate Affiliation): Liberal participants indicate higher degrees of support for liberal candidates than conservative candidates (diff = .789, *p* < .001).  [1,1 - 1,2]

Main Effect (Participant Affiliation): Conservative candidates recieve higher levels of support from conservative participants than they do liberal participants (diff = 1.40, *p* < .001). [1,2 - 2,2]

Interaction Effect: Conservative participants indicate higher degrees of support for their in-group candidates than libeals participants indicate for their in-group candidates (diff = .607, *p* = .002).   [1,1 - 2,2]

Interaction Effect: Conservative participants indicate a higher degree of support for their out-group candidates than liberals do for their out-group candidates (diff = .906, *p* < .001).  [2,1 - 1,2]